Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-02 manuscript.Rmd
Add raw event time series plots

The raw social cohesion time series can be seen in Figure \@ref(fig:raw-cohesion).

@@

>>>>

The raw social cohesion time series can be seen in Figure \@ref(fig:raw-cohesion-ts).

@@

The raw event time series for target filtered data can be seen in Figure \@ref(fig:raw-event-ts-target). The The raw event time series for source and target filtered data can be seen in Figure \@ref(fig:raw-event-ts-source-target).

```{r raw-event-ts-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap="Raw event count time series for target filtered data."}

# read in social cohesion data
event_df <- read.csv("./data/formatted/primary/formatted_data.csv")

# plot the time series
ggplot() +
  geom_line(event_df, mapping = aes(x= as.Date(Date), y=all_events_target, colour = 'all events')) +
  geom_line(event_df, mapping = aes(x= as.Date(Date), y=pos_events_target, colour = 'positive events')) +
  geom_line(event_df, mapping = aes(x= as.Date(Date), y=neg_events_target, colour = 'negative events')) +
  scale_color_manual(values = c("red", "orange", "blue")) +
  xlab("Date") +
  ylab("Number of events") +
  ylim(0, 360)

ggsave("./results/primary/raw-event-ts-target.png")

# call the image
knitr::include_graphics("./results/primary/raw-event-ts-target.png")

```{r raw-event-ts-source-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap="Raw event count time series for source and target filtered data."}

# plot the time series
ggplot() +
  geom_line(event_df, mapping = aes(x= as.Date(Date), y=all_events_source_target, colour = 'all events')) +
  geom_line(event_df, mapping = aes(x= as.Date(Date), y=pos_events_source_target, colour = 'positive events')) +
  geom_line(event_df, mapping = aes(x= as.Date(Date), y=neg_events_source_target, colour = 'negative events')) +
  scale_color_manual(values = c("red", "orange", "blue")) +
  xlab("Date") +
  ylab("Number of events") +
  ylim(0, 360)

ggsave("./results/primary/raw-event-ts-source-target.png")

# call the image
knitr::include_graphics("./results/primary/raw-event-ts-source-target.png")
